Temperature Measurements in Optical Tweezer Experiments

### 2017-01-10 doc/draft1.tex
added renderings, more draft

@@

@@

\newpage
\section{Results}
% results with different parameters, graphs, etc.
Since the simulation consists of various parts that have to work together, we first need to check if every part itself works.\\
\subsection{The Crystal}
The first element of the simulation is the setup of the FCC lattice on which the particles are placed on. To check if this is done correctly, we can
use a visualisation and rendering software such as VMD\cite{Humphrey1996} or OVITO\cite{Stukowski2010}. The rendered image of the nano crystal 
can be seen in fig.~\ref{fig:glass}. The chosen perspective shows the structure of the FCC lattice, where 3 layers are forming 
where the atoms take the position on the gap between the atoms from the layer below.\\
\begin{figure}[h]
    \begin{center}
        \includegraphics[scale=0.2]{images/fcc_rendering_new.png}
        \caption{Rendering of the model of the nano crystal before starting the simulation. 
                    The perspective shows the 3 layers of the FCC lattice. These layers consist of atoms
                    taking the position above the gap between two of the atoms from the layer below and match the positions of the atoms 2 layers
                below. The black box is the outline of the particles' positions and shows the geometry of the system.}
        \label{fig:glass}
    \end{center}
\end{figure}

>>>>

\label{section:verlet}

@@

\subsection{The Laser Beam - Trapping}
As mentioned above, the glass particle is trapped in the laser beam and the motion of the particle is suppressed in every direction. This behaviour
has to be modeled as well.\\
The approximation of the original paper \cite{Gieseler2014}, where the movements in the three spatial directions are decoupled will be
used in the model as well. As to the model of the trapping force itself, the most straightforward approach is to use a harmonic oscillator potential.
The force and the corresponding potential can be written as
\begin{eqnarray}
    \mathbf{F} &=& -k x\\
    U &=& \frac12 k x^2
\end{eqnarray}
The trap is implemented by using the velocity Verlet algorithm with the above force to propagate the glass particle. Since the trap is acting on the
whole system, the force is acting on the center of mass position and velocity. To calculate the center of mass positions and velocities, the positions
and velocities of all particles have to be summed up and divided by the particle number:
\begin{eqnarray}
    \mathbf{r}_\text{COM} &=& \sum_{i=1}^N \frac{\mathbf{r}_i}{N}\\
    \mathbf{v}_\text{COM} &=& \sum_{i=1}^N \frac{\mathbf{v}_i}{N}
\end{eqnarray}
The position of the center of mass and the center of mass velocity are then propagated by using the same procedure as introduced in
section~\ref{section:verlet}.

@@

\newpage
\section{Results}
% results with different parameters, graphs, etc.
Since the simulation consists of various parts that have to work together, we first need to check if every part itself works.\\
\subsection{The Crystal}
The first element of the simulation is the setup of the FCC lattice on which the particles are placed on. To check if this is done correctly, we can
use a visualisation and rendering software such as VMD\cite{Humphrey1996} or OVITO\cite{Stukowski2010}. The rendered image of the nano crystal 
can be seen in fig.~\ref{fig:glass}. The chosen perspective shows the structure of the FCC lattice, where 3 layers are forming 
where the atoms take the position on the gap between the atoms from the layer below.\\
\begin{figure}[h]
    \begin{center}
        \includegraphics[scale=0.2]{images/fcc_rendering_layer_newcoloring.png}
        \caption{A rendered image of the FCC crystal. The chosen color-coding along the (1,1,1) Miller-index 
                highlights the layers for this perspective. The perspective is
                chosen to see the layering of the FCC crystal with its 3 layer structure. The black box acts as a reference point to outline the 
                geometry of the system.}
            %Rendering of the model of the nano crystal before starting the simulation. 
            %The chosen perspective shows the 3 layers of the FCC crystal with a
                    %These layers consist of atoms
                    %taking the position above the gap between two of the atoms from the layer below and match the positions of the atoms 2 layers
                %below. The black box is the outline of the particles' positions and shows the geometry of the system.}
        \label{fig:glass}
    \end{center}
\end{figure}

\subsection{Velocity Verlet}
The simulation is taking place in a NVE ensemble from a thermodynamic point of view. This means that the particle number $N$, the volume $V$ and the
total energy $E$ are constant. In contrast to the NVT ensemble used in Monte-Carlo simulations this means, that the velocities of the particle can not
be chosen directly. The initial velocities have to be drawn from a random number generator. This means that the velocities have to be adjusted after 
they have been drawn.\\
The first adjustment that needs to be made is making sure that the system is staying in place and not floating away. To do this, the velocity vectors
of all the atoms in the system have to be added to get the resulting velocity vector for the whole system that is thought to be acting on the center
of mass. This resulting vector is then divided by the number of particles in the system and the resulting vector is then subtracted from every
velcocity vector of every atom in the system. 
\begin{eqnarray}
    \mathbf{v}_\text{tot} &=& \sum_{i=1}^N \mathbf{v}_i\\
    \mathbf{v}_\text{cut} &=& \frac{\mathbf{v}_\text{tot}}N\\
    \mathbf{v}_i^\text{new} &=& \mathbf{v}_i - \mathbf{v}_\text{cut}
\end{eqnarray}
The next adjustment is a small one that makes a difference in the long run. When choosing random velocities, the system not only tends to have a
resulting velocity vector that causes the whole system to float away, but also a resulting angular momentum that causes the system to rotate.
The angular momentum can be defined via the moment of inertia $\mathbf{I}$
\begin{eqnarray}
    \mathbf{L} &=& \mathbf{I}\boldsymbol{\omega}\\
    \boldsymbol{\omega} &=& \frac{\mathbf{r} \times \mathbf{v}}{r^2}
\end{eqnarray}
where $\boldsymbol{\omega}$ is the angular velocity of the system. 
\\The velocities of the particle can roughly be chosen by adjusting the range of numbers the random number generator can choose from. However, the
resulting velocities (and therefore the temperature of the system) are generally not precisely how they should be. If the system should have a
specific starting temperature $T$, the velocities need to be scaled accordingly. This rescaling is done by summing the square of the velocities
(this equals calculating the kinetic energy since the masses are set to 1) and rescale them by a factor $\lambda$:
\begin{eqnarray}
    E &=& \sum_{i=1}^N \mathbf{v}_i^2\\
    \lambda &=& \sqrt{\frac{3(N-1)T}{E}}\\
    \mathbf{v}_i^\text{new} &=& \lambda \mathbf{v}_i 
\end{eqnarray}
This process has to be done a couple of times, until the system equilibrates to the desired temperature. The problem with this procedure is the fact
that it contradicts the constant energy property of the ensemble. If we look at the energy values in fig.~\ref{fig:energystart} we can see the
irregularities before the system equilibrates to a constant value.

%\begin{figure}[h]
    %\begin{center}
        %\begin{subfigure}[t]{0.3\textwidth}
            %\includegraphics[scale=0.3]{images/fcc-2.pdf}
            %\caption{Schematic figure of a face centered cubic (FCC) lattice}
            %\label{fig:fcc}
        %\end{subfigure} 
        %\
        %\begin{subfigure}[t]{0.3\textwidth}
            %\includegraphics[scale=0.15]{images/fcc_unit.png}
            %\caption{Schematic of the number of particles contained in one FCC unit cell. The atoms on the edges are shared by 8 cells and the ones 
                %on the faces by 2 cells\cite{unitcell}}
            %\label{fig:fcccut}
        %\end{subfigure} 
        %\
        %%\hspace{60pt}
        %\begin{subfigure}[t]{0.3\textwidth}
            %\includegraphics[scale=0.3]{images/unit_cell.pdf}
            %\caption{Setup for successively building a FCC lattice}
            %\label{fig:unitcell}
        %\end{subfigure}
    %\end{center}
%\end{figure}
